### 2015-03-18 staticanalysis.tex
fixed an example

\begin{boogie}
procedure ep1(dev: int) modifies $M.0; {
  var $p0, $p1, $p2, $p3, $p4, $p5, $p6: int;
  $bb0:
    \textbf{$p0 := dev;}
    $p1 := $pa($p0, 32, 1);
    $p2 := $pa($pa($p1, 0, 24), 12, 1);
    $p3 := $pa($pa($p2, 0, 12), 0, 1);
    call _UPDATE_CLS_$ep1(lock$0, true);
    $p4 := $pa($pa($p1, 0, 24), 4, 1);
    call _WRITE_LS_$M.0_$ep1($p4);
    $p5 := $pa($pa($p1, 0, 24), 12, 1);
    $p6 := $pa($pa($p5, 0, 12), 0, 1);
    call _UPDATE_CLS_$ep1(lock$0, false);
    return;
}
\end{boogie}

>>>>

\begin{boogie}
procedure ep1(dev: int) modifies $M.0; {
  var $p0, $p1, $p2, $p3, $p4, $p5, $p6: int;
  $bb0:
    $p0 := dev;
    $p1 := $pa($p0, 32, 1);
    $p2 := $pa($pa($p1, 0, 24), 12, 1);
    $p3 := $pa($pa($p2, 0, 12), 0, 1);
    call _UPDATE_CLS_$ep1(lock$0, true);
    $p4 := $pa($pa($p1, 0, 24), 4, 1);
    call _WRITE_LS_$M.0_$ep1($p4);
    $p5 := $pa($pa($p1, 0, 24), 12, 1);
    $p6 := $pa($pa($p5, 0, 12), 0, 1);
    call _UPDATE_CLS_$ep1(lock$0, false);
    return;
}
\end{boogie}
